### 2022-08-05 paper/akweury/document.tex
update paper

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{float}
\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{rotating}
\usetikzlibrary{fit}
\usetikzlibrary{calc,patterns,angles,quotes}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

@@

	\begin{tikzpicture} 
		% reference lines
		\coordinate (light) at (-1,3);
		\coordinate (p) at (2,0);
		\coordinate (normal) at (2,3);
		\draw [fill=blue!20] plot [smooth cycle] coordinates {(0,0) (1,1) (3,1) (5,0) (2,-1)}; %% surface element
		\draw[thick, ->] (2,0) -- (2,3) node[midway, left] {$ \textbf{n} $}; %% normal
		\draw[thick, ->] (2,0) -- (-1,3) node[midway, left] {$ \textbf{l} $}  ; %% source direction
		\pic [draw, ->, "$\theta$", angle eccentricity=1.5] {angle = normal--p--light};
		\draw[thick, ->] (2,0) -- (5,3) node[midway, left] {$ \textbf{v} $}; %% view direction
		\filldraw[black] (-1,3) circle (2pt) node[anchor=south west]{light source}; %% light source
		\filldraw[black] (5,3) circle (2pt) node[anchor=south west]{view point}; %% view point		
	\end{tikzpicture}
	\caption{The surface normal, source light direction and the view point direction, where $ \theta $ denotes the angle between light direction and the normal.}
	\label{fig:lambertian-surface}
\end{figure}

\end{document}

>>>>

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography
\usepackage{import}
\usepackage{float}
\usepackage{tikz}
\usepackage{tikz-network}
\usepackage{breqn}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage{rotating}
\usetikzlibrary{fit}
\usetikzlibrary{calc,patterns,angles,quotes}
\usetikzlibrary {arrows.meta,graphs,shapes.misc}
\usetikzlibrary {positioning}

@@

\begin{tikzpicture}
	\pgfplotsset{ticks=none}
	\begin{axis} [axis lines=center]
		\addplot [domain=0:1, smooth, thick, width=5mm, color=red] { x };
		\addplot [domain=1:2, smooth, width=5mm] { x };
		\addplot [domain=-2:-1, smooth, width=3mm] { -x };
		\addplot [domain=-1:0, smooth, thick, width=3mm, color=red] { -x };
		\addplot [domain=-2:-1, smooth, thick, color=red] { (x^2+1^2)/(2*1) };
		\addplot [domain=1:2, smooth, thick, color=red] { (x^2+1^2)/(2*1) };
	\end{axis}
\end{tikzpicture}
	\caption{The shape of Berhu Loss (show in red line). }
	\label{fig:berhu-loss-shape}
\end{figure}
\end{document}
